### 2016-08-23 rebuttal.tex

\question Lines 359 and 379: what is 2D text representation? It seems that ``2D'' shouldn't be here.
\begin{solution}
This sentence was replaced with:
\begin{quote}
A two-dimensional (2D) textual representation of the expression can
be printed with monospace fonts via \verb|pprint|.
\end{quote}
We use here the same terminology as in the Mathematica
online documentation, e.g., the
\href{https://reference.wolfram.com/language/ref/OutputForm.html}{\texttt{OutputForm}}
function:
\begin{quote}
\texttt{OutputForm[expr]}: prints as a two-dimensional representation of expr using only keyboard characters.
\end{quote}
\end{solution}

\question Line 427: every dictionary is a ``dictionary of keys''. This should be a dictionary with coordinate tuples as keys associated with the appropriate values.
\begin{solution}
``Dictionary of Keys'' (DOK) refers specifically to a sparse matrix
representation where entries are stored as \texttt{(row, column)} pairs
mapping to the elements. See for instance \texttt{scipy.sparse.dok\_sparse}. We
have fixed the capitalization of ``Dictionary of Keys'' and added the
abbreviation (DOK), and stated explicitly what is meant by this. We have also
made a similar note about List of Lists (LIL) earlier in the section.
\end{solution}

\question Section 4 would benefit from an introduction, and lines 440-- should become a new subsection 4.1. (named ``Float'' or ``Real numbers support'' or similar).
\begin{solution}
We have added an introduction and a subsection ``Floating-Point Numbers''
(which, for mathematical clarity, we consider to be distinct from ``real
numbers'').
\end{solution}

@@

\question The title of section 5, ``Domain specific submodules'', seems inappropriate because the section only covers Physics package (not ``submodules''). It should either be expanded with a short introduction listing other domain specific packages, or it should be renamed to ``Physics package''.
\begin{solution}
  % TODO: Should we rename it to "Physics submodules"?
(see also the discussion at~\ref{rev1point37}).
\end{solution}

\question The word ``symbolics'' in line 528 should be removed (as almost everything in the paper deals with symbolic computation).
\begin{solution}
We have done this.
\end{solution}

\question In line 530, sympy.physics.vector is a module, not a package.
\begin{solution}
The word ``package'' replaced with ``submodule'' (see also point~\ref{rev1point37}).
\end{solution}

\question It is unclear what ``both of these objects'' refer to in line 532. My guess is vectors and dyadic objects, but this should be reworded to make it more clear.
\begin{solution}
We have changed ``both of these objects can be written\ldots'' to ``the vector
and dyadic objects can both be written\ldots''.
\end{solution}

### 2016-08-23 domain_specific.tex
Address reviewer 3 point 33

The \verb|sympy.physics.vector| submodule provides reference frame-, time-, and
space-aware vector and dyadic objects that allow for three-dimensional
operations such as addition, subtraction, scalar multiplication, inner and
outer products, and cross products. Both of these objects can be written in
very compact notation that make it easy to express the vectors and dyadics in
terms of multiple reference frames with arbitrarily defined relative
orientations. The vectors are used to specify the positions, velocities, and
accelerations of points; orientations, angular velocities, and angular
accelerations of reference frames; and forces and torques. The dyadics are
essentially reference frame-aware $3 \times 3$ tensors~\cite{tai1997generalized}.
The vector and dyadic
objects can be used for any one-, two-, or three-dimensional vector algebra, and
they provide a strong framework for building physics and engineering tools.

>>>>

The \verb|sympy.physics.vector| submodule provides reference frame-, time-,
and space-aware vector and dyadic objects that allow for three-dimensional
operations such as addition, subtraction, scalar multiplication, inner and
outer products, and cross products. The vector and dyadic objects can both be
written in very compact notation that make it easy to express the vectors and
dyadics in terms of multiple reference frames with arbitrarily defined
relative orientations. The vectors are used to specify the positions,
velocities, and accelerations of points; orientations, angular velocities, and
angular accelerations of reference frames; and forces and torques. The dyadics
are essentially reference frame-aware $3 \times 3$
tensors~\cite{tai1997generalized}. The vector and dyadic objects can be used
for any one-, two-, or three-dimensional vector algebra, and they provide a
strong framework for building physics and engineering tools.
